---
title: "R-markdown"
author: "Enoch Alex"
date: "`r Sys.Date()`"
output: html_document
---




```{r load-data, message=FALSE}
library(tidyverse)
library(kableExtra)
library(rmarkdown)
library(ggpubr)
#load the dataset
pop_data <- read.csv("data/gapminder_data.csv")

#create a table with data from European countries in 2007 showing the countries with the largest life expectancy
euro_data_tbl <- pop_data %>%
                    filter(continent == "Europe" & year ==2007) %>%
                    select(-continent, -year) %>%
                    arrange(desc(lifeExp)) %>%
                    rename("Country" = country, "Population Size" = pop,
                           "Life Expectancy" = lifeExp, "GDP" = gdpPercap)
  
```
# Here we have our dataset
```{r creat-table}

euro_data_tbl %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
```{r creat-table-2}
euro_data_tbl %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
```{r}
euro_data_tbl %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", font_size = 1))
```
Here is an example of how to display a massive table
```{r paged-table}
paged_table(euro_data_tbl)
```
Next, the life expectancy in Europe is observed across different years.  The aim of this is to check if there was a change in life expectancy over the years.  The data used for the life expectancy over the years analysis is the gapminder data and the following data manipulation was performed:

```{r fig-data}
#keep on European data and change year to factor
euro_data_fig <- pop_data %>% 
                    filter(continent == "Europe")  %>% 
                    mutate(year=as_factor(year))
```

The life expectancy for Europe over the years is plotted as following:

```{r fig, warning=FALSE, fig.cap="Life Expectancy in Europe over the years"}
#Euro plot
euro_plot <- euro_data_fig %>%
                ggplot(mapping=aes(x=year, y=lifeExp)) +
                geom_violin() +
                stat_summary(fun.y = median, geom = "point")

#draw euro plot
euro_plot
```
!
